Comparing Results with Mafessoni et al.

### 2019-07-10 PlottingScripts/ProcessPlotData.Rmd
updated figure 1
squared fig1

#toggle for all snps or just JPT 1kGP snps
name <-''#'strict.gcat.' #'gcat.' # '' #

@@

jpt_imp$dist_2 <- round(jpt_imp$dist, -1)

@@

ggsave(paste0(figurePath,
              "Imputation_Distance_100s_gw.jpg"),
       height = 9,
       width = 9)
```

>>>>

#toggle for all snps or just JPT 1kGP snps
name <-'strict.gcat.' #'gcat.' # '' #

@@

jpt_imp$dist_2 <- round(jpt_imp$dist, -3)

@@

ggsave(paste0(figurePath,
              "Imputation_Distance_1000s_gw.jpg"),
       height = 9,
       width = 9)
```

### 2019-07-10 PlottingScripts/ProcessedData/ScoopCheck.Rmd
squared fig1

p_comp
```
```{r}
#missing in Mafessoni
p <- to_plot %>%
  filter(strict_mask == 'Pass')

@@

#missing in Mafessoni
f <- to_plot %>%
  filter(strict_mask == 'Fail')

>>>>

p_comp
```
```{r}
#missing in Mafessoni
p <- to_plot %>%
  filter(strict_mask == 'Pass strict mask')

@@

#missing in Mafessoni
f <- to_plot %>%
  filter(strict_mask == 'Fail strict mask')
